SOURCE SEPARATION METHODS FOR COMPUTER-ASSISTED ORCHESTRATION

### 2021-06-14 source_separation/paper/paper.tex
Add suggestions from Helene-Camille

	Orchestration is hard to define, however one could say that orchestration is the set of musical writing techniques that focus on timbre, or \textit{tone color} of the sound. A simplistic  definition of musical orchestration would be to say that it consists of the distribution of the different musical voices of a piece to the instruments of the orchestra. Orchestration has been traditionally taught in an intuitive and non-formalized way, and computer-assisted orchestration seeks to help composers by accelerating certain creative processes.

@@

%  The codebase for this paper can be found at: \url{https://github.com/dzluke/MLSP2021}, and you can listen to a selection of targets and orchestrations here: \url{https://dzluke.github.io/MLSP2021/}.
  The codebase for this paper can be found at: \url{anonymous}, and you can listen to a selection of targets and orchestrations here: \url{anonymous}.

@@

  We compare the effectiveness of different source separation methods for the task of orchestration by applying the separation methods to various targets, orchestrating the separated output of the method, and finally comparing this to the orchestration of the target if no separation was performed (see Fig. \ref{fig:full_diagram}). Following the previous example, consider a target sound that is a combination of a low droning sound and high-pitched whistle. With separation, these two sounds would be disentangled into two separate sub-targets and each would be individually orchestrated. The separated orchestrations would then be combined to create the solution. This would then be compared to the orchestration if no separation had been performed.

>>>>

	Orchestration~\cite{adler1989study} is hard to define, however one could say that orchestration is the set of musical writing techniques that focus on timbre, or \textit{tone color} of the sound. A simplistic  definition of musical orchestration would be to say that it consists of the distribution of the different musical voices of a piece to the instruments of the orchestra. Orchestration has been traditionally taught in an intuitive and non-formalized way, and computer-assisted orchestration seeks to help composers by accelerating certain creative processes.

@@

%  The codebase for this paper can be found at: \url{https://github.com/dzluke/MLSP2021}, and you can listen to a selection of targets and orchestrations here: \url{https://dzluke.github.io/MLSP2021/}.
  The codebase for this paper can be found at: \url{anonymous}, and a selection of targets and orchestrations are available for listenig at: \url{anonymous}.

@@

  We compare the effectiveness of different source separation methods for the task of orchestration by applying the separation methods to various targets, orchestrating the separated output of the method, and finally comparing this to the orchestration of the target if no separation was performed (see Fig. \ref{fig:full_diagram}). Following the previous example, consider a target sound that is a combination of a low droning sound and high-pitched whistle. With separation, these two sounds would be disentangled into two separate sub-targets and each would be individually orchestrated. The separated orchestrations would then be combined to create the solution. This would then be compared to the orchestration when no separation had been performed.
